gtsummary

### 2020-12-09 rmarkdown-gtsummary.Rmd
Update rmarkdown-gtsummary.Rmd

```{r}
trial %>%
  imap_dfr(
    ~tibble(
      colname = .y, 
      label = attr(.x, "label"), 
      class = class(.x), 
      values = trial %>% select(.y) %>% distinct() %>% 
        arrange(!!rlang::sym(.y)) %>% slice(1:4) %>% pull(.y) %>% 
        na.omit() %>% {paste("`", ., "`", collapse = ", ")}
    ) %>%
      mutate(
        values = ifelse(length(unique(na.omit(trial[[.y]]))) > 4,
                        paste(values, ", ..."),
                        values) 
      )
  ) %>%
  knitr::kable(caption = "Example data frame, `trial`") 
```

>>>>

```{r}
tbl_trial_desc <- 
  trial %>%
  imap_dfr(
    ~tibble(
      colname = .y, 
      label = attr(.x, "label"), 
      class = class(.x), 
      values = trial %>% select(.y) %>% distinct() %>% 
        arrange(!!rlang::sym(.y)) %>% slice(1:4) %>% pull(.y) %>% 
        na.omit() %>% {paste("`", ., "`", collapse = ", ")}
    ) %>%
      mutate(
        values = ifelse(length(unique(na.omit(trial[[.y]]))) > 4,
                        paste(values, ", ..."),
                        values) 
      )
  )

tbl_trial_desc %>%
  knitr::kable(caption = "Example data frame, `trial`")

tbl_trial_desc %>%
  gt(caption = "Example data frame, `trial`") %>%
  fmt_markdown(everything()) %>%
  as_latex() %>%
  as.character() %>%
  cat() %>%
  readr::write_lines("tbl_trial_desc.tex")
```
